Historical trends in the contribution of six major causes of death to the black-white

### 2017-04-17 Manuscript/Manuscript_COD_Trends.Rmd

```{r load_data, echo=F}
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")

cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")

cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))
```

>>>>

```{r load_data, echo=F}
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map(BlackWhite_results, "state", "stabbrs")
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map(cod_decomp_results, "state", "stabbrs")
cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))
```
